Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 measurements.tex
Extract some figures for the results

\subsubsection{Encoding}
\includepdf[pages={31-32,38,40}]{images/raspberry.pdf}

\subsubsection{Decoding}
\includepdf[pages={29-30,34,36}]{images/raspberry.pdf}

>>>>

\subsubsection{Encoding}
%\includepdf[pages={31-32,38,40}]{images/raspberry.pdf}

% \begin{figure}[ht!]
% \centering
% \includegraphics[width=0.7\textwidth]{}
% \caption{Gooput measurements for the \ac{Raspi} 1. $q = 2$}
% \label{goodput_enc_rasp1}
% \end{figure}

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net14}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net24}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net34}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net44}
    \end{subfigure}
    \caption[ The average and standard deviation of critical parameters ]
    {\small The average and standard deviation of critical parameters: Region R4} 
    \label{fig:mean and std of nets}
\end{figure*}

\subsubsection{Decoding}
%\includepdf[pages={29-30,34,36}]{images/raspberry.pdf}

### 2016-06-05 metrics.tex
Extract some figures for the results

\subsubsection{Average Power Expenditure}
To extract the average power for a given configuration in our setup, we
first calculate the average current in each the idle state $I_{idle,avg}$
and the processing state $I_{idle,avg}$ for all the available sample for
the given configuration. Regardless of the current type, the average value
of the sample set of a given number of samples $N_s$ is:
%
\begin{align} \label{eq:avg_current}
I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Amperes}]
\end{align}
%
With the average current from \eqref{eq:avg_current}, we compute the average
current used for processing with respect to the idle state, by substracting
$I_{idle,avg}$ from $I_{proc,avg}$. Then, the result is multiplied by the
supply voltage to obtain the average power during the considered configuration,
given as:
%
\begin{align} \label{eq:avg_power}
P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watts}]
\end{align}
%
\subsubsection{Energy per Bit Consumption}
To get this metric for a given configuration, we simply express the energy
as the product of the average power by the processing time $T_{proc}$ obtained
from the goodput measurement for the same configuration. In this way, we can
relate the processing time by the goodput, the packet and the generation size
as shown:
%
\begin{align} \label{eq:goodput}
E_b = P_{avg} T_{proc} = P_{avg} \times \frac{g(B/8)}{R_{proc}} ~[\mathrm{Joules/bit}]
\end{align}
%

>>>>

\subsubsection{Average Power Expenditure}
To extract the average power for a given configuration in our setup, we
first calculate the average current in each the idle state $I_{idle,avg}$
and the processing state $I_{idle,avg}$ for all the available sample for
the given configuration. Regardless of the current type, the average value
of the sample set of a given number of samples $N_s$ is:
%
\begin{align} \label{eq:avg_current}
I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Amperes}]
\end{align}
%
With the average current from \eqref{eq:avg_current}, we compute the average
current used for processing with respect to the idle state, by substracting
$I_{idle,avg}$ from $I_{proc,avg}$. Then, the result is multiplied by the
supply voltage to obtain the average power during the considered configuration,
given as:
%
\begin{align} \label{eq:avg_power}
P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watts}]
\end{align}
%
\subsubsection{Energy per Bit Consumption}
To get this metric for a given configuration, we simply express the energy
as the product of the average power by the processing time $T_{proc}$ obtained
from the goodput measurement for the same configuration. In this way, we can
relate the processing time with the goodput, the packet and the generation size
as shown:
%
\begin{align} \label{eq:goodput}
E_b = P_{avg} T_{proc} = P_{avg} \times \frac{g(8B)}{R_{proc}} ~[\mathrm{Joules}]
\end{align}
%
